Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
more on notations
use macro
fill in all rules in S(C)

\newcommand{\sOOinspect}[3]{\mathtt{Eval} \; #2(#1) \; #3}
\newcommand{\sOOreturn}[2]{\mathtt{Cont} \; #2 \; #1}
\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}

@@

\newcommand{\kOOmt}[0]{\square}
\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; #2(#1) ]}
\newcommand{\kOOconsII}[2]{#2[\mathtt{cons} \; #1 \; \square]}
\newcommand{\kOOinl}[1]{#1[\mathtt{inl} \; \square]}
\newcommand{\kOOinr}[1]{#1[\mathtt{inr} \; \square]}
\newcommand{\kOOappI}[3]{
	#3[\square \; #2(#1) ]
}
\newcommand{\kOOappII}[2]{
	#2[#1 \; \square]}
\newcommand{\kOOcar}[1]{#1[\mathtt{fst} \; \square]}
\newcommand{\kOOcdr}[1]{#1[\mathtt{snd} \; \square]}
\newcommand{\kOOcaseI}[4]{
	#4[\mathtt{case} \; \square \; #3(#1) \; #3(#2) ]}
\newcommand{\kOOcaseII}[4]{
	#4[\mathtt{case} \; #1 \; \square \; #3(#2) ]}
\newcommand{\kOOcaseIII}[3]{
	#3[\mathtt{case} \; #1 \; #2 \; \square]}
\newcommand{\kOOcast}[2]{
	#2[\square \langle #1 \rangle]}

@@

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
\newcommand{\continue}[2]{continue(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

The transition relation $\judgeCreduce{s}{s}$ is parameterized over
$applyCast$ to allow for the differences between D and UD.
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%% Other
%% transition rules starting from$Eval$states are standard.
To apply a casted function, the machine first casts $v_1$, the
operand, then applies the casted operand to $v_2$, the underlying
function, and finally cast the result of the function application.
%
To take out the first (resp. second) part of a casted pair, the
machine firstly take out the first (resp. second) part of $v$, the
underlying pair, and cast the result.
%
In case splitting, if the target value is a left injection, the
machine moves to a state that will apply the first continuation
function to the value inside the left injection. The case for right
injection is similar.
%
When the target value is a casted sum, the machine moves the cast from
the target value to continuations functions.
%
To cast a value, the machine invokes $applyCast$ on the value.  If the
cast succeeds, the machine returns the result to the next
continuation.  If the cast fails, the machine halts with the blame
label.
%
%% When the continuation is $stop$, the machine enters a halting
%% state. The When the machine is in a halting state, it stays in the
%% same state.

@@

\redrule{
	\highlight{\sOOreturn{v_3}{(\mathtt{case_3}\;
		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
		\;v_2\;\kappa)}}
}{
	\highlight{\sOOreturn{v_3'}{
		(\mathtt{case_3}\;v
		\;v_2'\;\kappa)
	}}
}{\\&&
\highlight{\text{where}\;
v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
\\&&
\highlight{\text{and}\;
v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
}

@@

To use our framework, users needs to prove that their cast representation
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}), a subset of 
Cast ADT. Property (1) 
states that $id(T)$acts like the identity function. Property (2) states 
that $seq(c,c)$acts like a sequence of casts. Properties (3) through 
(11) state that $cast(T_1,l,T_2)$act like the Lazy D$applyCast$
defined in Fig.~\ref{fig:applyCast-D-C}.

@@

	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
	\[
	\begin{array}{rclr}
	\hiredruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho[x]}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOtt}{\kappa}
	}{}
	\hiredruleS{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{cont(\kOOinl{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{cont(\kOOinr{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\kOOappI{E}{e_2}{\kappa})}}{}

@@

\hifunrule{
	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
\begin{cases}
	\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
\\
\sOOhalt{l} \\
\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
\end{cases}
}{}
\hifunrule{
	\continue{v_3}{(\mathtt{case_3}\;(\hcvOOinl{v}{c})\;
		(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})
		\;\kappa)}
}{
	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
}{}

@@

\todoKC{describe transition rules}
We list a fraction of reduction rules due to space limitation.
\todo[inline]{Don't omit reduction rules, instead put some in the appendix. -JS}
When values are constructed, their hypercoercion parts are filled with outputs 
of $id$. For instance, when a function value is constructed, its first part 
and last part are initialized to $id(T_1)$ and $id(T_2)$respectively.
When evaluating a cast expression, the current continuation is extended with a 
hypercoercion constructed by $cast$. $ext$ composes the new hypercoercion 
with the hypercoercion on the top of the continuation.
When evaluating a compound expression, the machine firstly construct the new 
pre-continuation, then turn it to a continuation by adding an identity 
hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
expression, the machine firstly construct $\hckOOconsI{e_2}{\rho}{\kappa}$, 
the new pre-continuation, then call $cont$, which adds an identity cast to 
form a continuation. 
When a function call happens, the machine firstly cast the operand. If the 
casting succeeds, the machine then evaluate the body in the extended 
environment and the extended continuation. If the casting fails, the machine 
then halts with the blame label.

>>>>

\newcommand{\sOOinspect}[3]{\langle\langle#1,#2\rangle,#3\rangle}
\newcommand{\sOOreturn}[2]{\langle#1,#2\rangle}
\newcommand{\sOOhalt}[1]{\mathtt{Halt} \; #1}

@@

\newcommand{\kOOmt}[0]{\square}
\newcommand{\kOOconsI}[3]{#3[\mathtt{cons} \; \square \; \langle#1,#2\rangle ]}
\newcommand{\kOOconsII}[2]{#2[\mathtt{cons} \; #1 \; \square]}
\newcommand{\kOOinl}[1]{#1[\mathtt{inl} \; \square]}
\newcommand{\kOOinr}[1]{#1[\mathtt{inr} \; \square]}
\newcommand{\kOOappI}[3]{
	#3[\square \; \langle#1,#2\rangle ]
}
\newcommand{\kOOappII}[2]{
	#2[#1 \; \square]}
\newcommand{\kOOcar}[1]{#1[\mathtt{fst} \; \square]}
\newcommand{\kOOcdr}[1]{#1[\mathtt{snd} \; \square]}
\newcommand{\kOOcaseI}[4]{
	#4[\mathtt{case} \; \square \; \langle#1,#3\rangle \; \langle#2,#3\rangle ]}
\newcommand{\kOOcaseII}[4]{
	#4[\mathtt{case} \; #1 \; \square \; \langle#2,#3\rangle ]}
\newcommand{\kOOcaseIII}[3]{
	#3[\mathtt{case} \; #1 \; #2 \; \square]}
\newcommand{\kOOcast}[2]{
	#2[\square \langle #1 \rangle]}

@@

\newcommand{\typingHC}[3]{#1 : #2 \Longrightarrow #3}
\newcommand{\hcvOOinj}[2]{\mathtt{inj} \; #2}
%\newcommand{\hcvOOfun}[5]{\mathtt{fun} \; #1 \; #2 \; #3 \; #4 \; #5}
\newcommand{\hcvOOfun}[5]{\mathtt{fun}^{\POOfun{#1}{#5}} \; #2 \; #3 \; #4}
\newcommand{\hcvOOtt}[0]{\mathtt{unit}}
%\newcommand{\hcvOOcons}[4]{\mathtt{cons}\;#1\;#2\;#3\;#4}
\newcommand{\hcvOOcons}[4]{\mathtt{cons}^{\POOprod{#2}{#4}}\;#1\;#3}
%\newcommand{\hcvOOinl}[2]{\mathtt{inl}\;#1\;#2}
%\newcommand{\hcvOOinr}[2]{\mathtt{inr}\;#1\;#2}
\newcommand{\hcvOOinl}[2]{\mathtt{inl}^{#2}\;#1}
\newcommand{\hcvOOinr}[2]{\mathtt{inr}^{#2}\;#1}
\newcommand{\hckOOmt}[0]{\mathtt{stop}}
\newcommand{\hckOOconsI}[3]{\mathtt{cons_1}\;#1\;#2\;#3}
\newcommand{\hckOOappII}[2]{\mathtt{app_2}\;#1\;#2}
\newcommand{\sidecond}[1]{\text{if}\;#1}
% Lazy D cast calculus on space-inefficient CEK
\newcommand{\judgeCreduce}[2]{#1 \longmapsto_{\mathcal{C}} #2}
\newcommand{\judgeCreduceTrans}[2]{#1 \longmapsto_{\mathcal{C}}^{*} #2}
\newcommand{\judgeCeval}[2]{eval_{\mathcal{C}}(#1) = #2}
\newcommand{\redrule}[3]{#1 & \longmapsto_\mathcal{C} & #2 & #3\\}
\newcommand{\hiredrule}[3]{\highlight{#1} & \highlight{\longmapsto_\mathcal{C}} & \highlight{#2} & \highlight{#3} \\}
% blame calculus on space-efficient CEK
\newcommand{\judgeSreduce}[3]{#2 \longmapsto_{\mathcal{S}(#1)} #3}
\newcommand{\judgeSreduceTrans}[3]{#2 \longmapsto_{\mathcal{S}(#1)}^{*} #3}
\newcommand{\judgeSeval}[3]{eval_{\mathcal{S}(#1)}(#2) = #3}
\newcommand{\redruleS}[3]{#1 & \longmapsto_{\mathcal{S}(C)} & #2 & #3\\}
\newcommand{\hiredruleS}[3]{\highlight{#1} & 
\highlight{\longmapsto_{\mathcal{S}(C)}} & \highlight{#2} & \highlight{#3} \\}
% Normal Coercion
\newcommand{\ncProj}[2]{#1?^{#2}}
\newcommand{\ncInj}[1]{#1!}
\newcommand{\ncId}[0]{\iota}
\newcommand{\ncSeq}[2]{#1;#2}
\newcommand{\ncFail}[1]{\bot^{#1}}
\newcommand{\ncFun}[2]{\POOfun{#1}{#2}}
\newcommand{\ncProd}[2]{\POOprod{#1}{#2}}
\newcommand{\ncSum}[2]{\POOsum{#1}{#2}}
% Hypercoercion
\newcommand{\hyperCoercionI}[0]{\mathtt{id\star}}
\newcommand{\hyperCoercionC}[3]{#1 \overset{#2}{\curvearrowright} #3}
% machine state simulations
\newcommand{\eqvS}[4]{#3 \approx_{\mathcal{S}\mathcal{S}} #4}
\newcommand{\eqvSD}[3]{#2 \approx_{\mathcal{SD}} #3}
% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}
\newcommand{\todoKCFixed}[0]{\todo[inline]{Fixed. -KC}}
% abbrev
\newcommand{\castCalculus}[0]{$\lambda_{\rightarrow}^{\langle\cdot\rangle}$}
% names
\newcommand{\ineffCEK}{$\mathcal{C}$}
\newcommand{\ineffCEKD}{$\mathcal{D}$}
\newcommand{\ineffCEKUD}{$\mathcal{UD}$}
\newcommand{\judgeDreduce}[2]{#1 \longmapsto_{\mathcal{D}} #2}
\newcommand{\judgeDreduceTrans}[2]{#1 \longmapsto_{\mathcal{D}}^{*} #2}
\newcommand{\judgeDeval}[2]{eval_{\mathcal{D}}(#1) = #2}
\newcommand{\judgeUDreduce}[2]{#1 \longmapsto_{\mathcal{UD}} #2}
\newcommand{\judgeUDreduceTrans}[2]{#1 \longmapsto_{\mathcal{UD}}^{*} #2}
\newcommand{\judgeUDeval}[2]{eval_{\mathcal{UD}}(#1) = #2}
\newcommand{\effCEK}[1]{$\mathcal{S}(#1)$}
\newcommand{\evalEqv}[2]{$eval_{\text{#1}} = eval_{\text{#2}}$}
\newcommand{\continue}[2]{continue(#2,#1)}
\newcommand{\highlight}[1]{{\color{red} #1}}

@@

The transition relation $\judgeCreduce{s}{s}$ is parameterized over
$applyCast$ to allow for the differences between D and UD.
%
When evaluating a cast expression, the machine moves the cast to the
continuation and evaluates the inner expression.
%% Other
%% transition rules starting from$Eval$states are standard.
To apply a casted function, the machine first casts $v_1$, the
operand, then applies the casted operand to $v_2$, the underlying
function, and finally cast the result of the function application.
%
To take out the first (resp. second) part of a casted pair, the
machine firstly take out the first (resp. second) part of $v$, the
underlying pair, and cast the result.
%
%In case splitting, if the target value is a left injection, the
%machine moves to a state that will apply the first continuation
%function to the value inside the left injection. The case for right
%injection is similar.
%
When the target value is a casted sum, the machine moves the cast from
the target value to continuations functions.
%
To cast a value, the machine invokes $applyCast$ on the value.  If the
cast succeeds, the machine returns the result to the next
continuation.  If the cast fails, the machine halts with the blame
label.
%
%% When the continuation is $stop$, the machine enters a halting
%% state. The When the machine is in a halting state, it stays in the
%% same state.

@@

\redrule{
	\highlight{\sOOreturn{v_3}{
		(	\kOOcaseIII{
				\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}}
			}{v_2}{\kappa})
%		
%			(\mathtt{case_3}\;
%		(\vOOcast{v}{\cOOcast{\POOsum{T_1}{T_2}}{l}{\POOsum{T_3}{T_4}}})
%		\;v_2\;\kappa)
	}}
}{
	\highlight{\sOOreturn{v_3'}{
			(\kOOcaseIII{v}{v_2'}{\kappa})
	}}
}{\\&&
\highlight{\text{where}\;
v2' = \vOOcast{v_2}{\cOOcast{\POOfun{T_4}{T}}{l}{\POOfun{T_2}{T}}}}
\\&&
\highlight{\text{and}\;
v3' = \vOOcast{v_3}{\cOOcast{\POOfun{T_3}{T}}{l}{\POOfun{T_1}{T}}}}
}

@@

To use our framework, users needs to prove that their cast representation
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}), a subset of 
Cast ADT. Property (1) 
states that $id(T)$acts like the identity function. Property (2) states 
that $seq(c,c)$acts like a sequence of casts. Properties (3) through 
(11) state that $cast(T_1,l,T_2)$act like the Lazy D $applyCast$
defined in Fig.~\ref{fig:applyCast-D-C}.

@@

	Reduction \fbox{$\judgeSreduce{C}{s}{s}$}
	\[
	\begin{array}{rclr}
	\hiredruleS{
		\sOOinspect{\eOOcast{e}{T_1}{l}{T_2}}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{ext(cast(T_1,l,T_2),\kappa)}
	}{}
	\redruleS{
		\sOOinspect{\eOOvar{x}}{\rho}{\kappa}
	}{	
		\sOOreturn{\rho(x)}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{\eOOsole}{\rho}{\kappa}
	}{
		\sOOreturn{\hcvOOtt}{\kappa}
	}{}
	\hiredruleS{
		\sOOinspect{\eOOlam{T_1}{T_2}{x}{e}}{\rho}{\kappa}
	}{
		\sOOreturn{(\hcvOOfun{id(T_1)}{\rho}{x}{e}{id(T_2)})}{\kappa}
	}{}
	\redruleS{
		\sOOinspect{(\eOOcons{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{E}{}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinl{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{cont(\kOOinl{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOinr{e})}{\rho}{\kappa}
	}{
		\sOOinspect{e}{\rho}{cont(\kOOinr{\kappa})}
	}{}
	\redruleS{
		\sOOinspect{(\eOOapp{e_1}{e_2})}{\rho}{\kappa}
	}{
		\sOOinspect{e_1}{\rho}{cont(\kOOappI{E}{e_2}{\kappa})}}{}

@@

\hifunrule{
	\continue{v_2}{(\kOOappII{(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})}{\kappa})}}{
\begin{cases}
	\sOOinspect{e}{\rho[x:=v']}{ext(c_2,\kappa)} \\
\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOsucc{v'}}
\\
\sOOhalt{l} \\
\;\;\;\;\;\sidecond{applyCast(v_2,c_1) = \rOOfail{l}}
\end{cases}
}{}

\hifunrule{
	\continue{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{
		\kOOcar{\kappa}
	}
}{
	\sOOreturn{v_1}{ext(c_1,k)}
}{}
\hifunrule{
	\continue{\hcvOOcons{v_1}{c_1}{v_2}{c_2}}{
		\kOOcdr{\kappa}
	}
}{
	\sOOreturn{v_2}{ext(c_2,k)}
}{}

\funrule{
	\continue{v_1}{\kOOcaseI{e_2}{e_3}{\rho}{\kappa}}
}{
	\sOOinspect{e_2}{\rho}{
		cont(\kOOcaseII{v_1}{e_3}{\rho}{\kappa})
	}
}{}

\funrule{
	\continue{v_2}{
		\kOOcaseII{v_1}{e_3}{\rho}{\kappa}
	}
}{
	\sOOinspect{e_3}{\rho}{
	\kOOcaseIII{v_1}{v_2}{\kappa}
	}
}{}

\hifunrule{
	\continue{v_3}{(\mathtt{case_3}\;(\hcvOOinl{v}{c})\;
		(\hcvOOfun{c_1}{\rho}{x}{e}{c_2})
		\;\kappa)}
}{
	\sOOreturn{v}{cont(\kOOappII{(\hcvOOfun{seq(c,c_1)}{\rho}{x}{e}{c_2})}{\kappa})}
}{}

@@

\todoKC{describe transition rules}
We list a fraction of reduction rules due to space limitation.
\todo[inline]{Don't omit reduction rules, instead put some in the appendix. -JS
\\---\\They are all in the figure. I haven't updated this paragraph 
accordingly. -KC}

%When evaluating a cast expression, the machine moves the cast to the
%continuation and evaluates the inner expression.
%To apply a casted function, the machine first casts $v_1$, the
%operand, then applies the casted operand to $v_2$, the underlying
%function, and finally cast the result of the function application.
%%
%To take out the first (resp. second) part of a casted pair, the
%machine firstly take out the first (resp. second) part of $v$, the
%underlying pair, and cast the result.
%%
%%In case splitting, if the target value is a left injection, the
%%machine moves to a state that will apply the first continuation
%%function to the value inside the left injection. The case for right
%%injection is similar.
%%
%When the target value is a casted sum, the machine moves the cast from
%the target value to continuations functions.
%%
%To cast a value, the machine invokes $applyCast$ on the value.  If the
%cast succeeds, the machine returns the result to the next
%continuation.  If the cast fails, the machine halts with the blame
%label.

The transition relation $\judgeSreduce{C}{s}{s}$ uses functions provides by $C$ 
to represent cases and to apply casts.
%
When evaluating a cast expression, the machine extends the continuation with 
cast $cast(T_1,l,T_2)$. The function $ext(c,\kappa)$ composes $c$ with the cast 
at the top of $k$ by calling $seq$.
%
To construct a function, the machine fills the casts $id$.
%
To return a value to a continuation, the machine first applies the top cast to 
the value. If the application fails, the machine halts with the blame label 
from the failure. Otherwise, the machine handles the pre-continuation with 
$continue$.
%
When the machine constructs a pair, a left injection, or a right injection, it 
fills the casts with $id$ as well, just like how it did for functions. 
%
To apply a function, the machine applies the domain cast $c_1$ to the 
operand $v_2$, extends the continuation with the codomain cast $c_2$, and 
evaluate the function body.
%
To take out the first (resp. second) part of a pair ...
%
%%In case splitting, if the target value is a left injection, the
%%machine moves to a state that will apply the first continuation
%%function to the value inside the left injection. The case for right
%%injection is similar.
%%
%When the target value is a casted sum, the machine moves the cast from
%the target value to continuations functions.
To case spliting a variant, ...

%When values are constructed, their hypercoercion parts are filled with outputs 
%of $id$. For instance, when a function value is constructed, its first part 
%and last part are initialized to $id(T_1)$ and $id(T_2)$respectively.
%When evaluating a cast expression, the current continuation is extended with a 
%hypercoercion constructed by $cast$. $ext$ composes the new hypercoercion 
%with the hypercoercion on the top of the continuation.
%When evaluating a compound expression, the machine firstly construct the new 
%pre-continuation, then turn it to a continuation by adding an identity 
%hypercoercion at the top. For instance, when evaluating a \texttt{cons} 
%expression, the machine firstly construct $\hckOOconsI{e_2}{\rho}{\kappa}$, 
%the new pre-continuation, then call $cont$, which adds an identity cast to 
%form a continuation. 
%When a function call happens, the machine firstly cast the operand. If the 
%casting succeeds, the machine then evaluate the body in the extended 
%environment and the extended continuation. If the casting fails, the machine 
%then halts with the blame label.
